comgen-outline

### 2017-09-03 paper/comgen-paper.Rmd
more on feature-probability, light edits to abstract

abstract: > 
    Generalizations are central to human understanding and language provides simple ways to convey generalizations (e.g., "Dogs bark").
    The language of generalizations is ubiquitous in everyday discourse and child-directed speech. 
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    The major issue in formalizing *genericity* is in determining what which such statements are true or false.
    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Dogs bark"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind"). 
    Across these diverse domains, we find that our model explains human endorsements of generalizations in language, while simpler models do not.
    This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
    The results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

keywords          : "genericity, generalizations, generics, pragmatics, semantics, bayesian modeling"
wordcount         : "X"

@@

If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability. 
One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
For generalizations, the threshold would apply to the *feature-probability* $h$:

@@

From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
]
Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. Rates are, of course, not constrained to be between 0 and 1 as probabilities are. 
However, a rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
]

@@

Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week)? 
We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
We separately measure endorsements under the same contexts (Expt. 2d) and use the prediction measurements (Expt. 2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.

@@

In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with some frequency.
To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.

@@

We next explore the endorsements of habituals from the items whose priors were measured the prior elicitation task.

@@

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression,
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "some_model",
                                      "habituals_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Speaker model - fixed semantics",
                                 "Speaker model - uncertain semantics",
                                 "Frequency alone", "Frequency + Distinctiveness"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")
```

@@

```{r habituals-endorsement-figure, fig.width=11, fig.height=8, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the (log) frequency of the referent action. Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on (log) frequency alone (lower left) and log frequency and distinctiveness (lower right). Bottom: Five example frequency priors and listener posteriors upon hearing the generalization. These distributions are inferred using both data sources from Expts. 2a & 2b.  (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})"}
grid.arrange(fig.habituals.endorsement.vs.freq, 
             habituals.endorsement.models,
             habituals.endorsement.insets, ncol = 2,
             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```

<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
For all analyses, we collapse across gender of the target character.
<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->

@@

#### Frequency baseline

The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is good is the frequency itself. 
This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence. 
First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g. \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
We see in addition that even when actions are done relatively frequently (e.g. 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g. \emph{wears socks}, \emph{drinks coffee}). 
In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g. between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
Overall, the raw log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
In addition, for actions that are done on the time scale of years or longer (lower median of frequency), frequency itself no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)

We observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.

#### Frequency and distinctiveness

In the prior elicitation task (Expt. 2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement. Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement. This is analagous to the regression model based on cue validity and prevalence in the domain of generics.

@@

We used the pragmatic speaker model $S_1$ (Eq. \ref{eq:S1}) with the priors elicited above (Expt. 2a) to predict felicity judgments in Expt. 2b, assuming the target propensity ($h$, to be conveyed by $S_1$) is the provided frequency (e.g., 3 times in the past year).
Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt. 2b.
To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->

@@

In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).

@@

While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
Does habitual language communicate propensity in terms of past frequency or future expectations?
On one hand, speakers can only *know* about what has happened in the past.
On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.

@@

<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
In Experiments 2c \& 2d, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt. 2c) and using that, with the model, to predict the felicity of habitual sentences (Expt. 2d). 
To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.

In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the propensity of the event.
Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic endorsement but not directly causally related.
In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the propensity prior is indeed causally related to generic endorsement.

@@

Language provides a way to bypass the observational data needed to make a causal induction.
Indeed, causal language has been shown to faciliate causal learning for nonobvious causal relations in 2-year-olds [@Bonawitz2010].

In this paper, we posit that prevalence priors are a mediating representation between abstract conceptual structure and generalizations in language.
In this last set of experiments, we test the causal relationship between the prevalence priors and endorsements of generalizations about causes.
Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.

@@

## Experiment 3a: Manipulating the Prevalence Prior for Causes

In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
This prediction task serves as a manipulation check for our prevalence prior manipulation.

@@

The experiment is a single-trial experiment with 2 phases to the trial.
In the first phase, participants are given a story about a causal domain.
In the second phase, participants are asked to make a judgment corresponding to the between-subjects condition they are assigned (prior, endorsement, interpretation).

@@

causals.endorsement.insets <- cas.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, 
                              levels = c("state_Prior","state_Posterior"),
                            labels = c("Listener Prior (Posterior given Silence)",
                                       "Listener Posterior given Causal")),
    Distribution = factor(distribution, 
                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
         labels = c("Common Deterministic", "Rare Deterministic",
                    "Common Weak", "Rare Weak"))) %>%
  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~Distribution, nrow = 1)+
  scale_fill_manual(values =inset.color.order )+
  scale_color_manual(values = inset.color.order)+
  scale_alpha_manual(values = c(0.1, 0.8))+
  scale_linetype_manual(values = c(2, 1))+
  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Prevalence") +
  ylab("Scaled probability density")+
  theme(legend.position = "bottom", legend.title = element_blank())+
  guides(fill = F, color = F)
```

@@

```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes. Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies. Bottom: Prevalence priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors. These distributions are inferred using both data sources from Expt. 3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
             layout_matrix = cbind(c(1,1,2)))

@@

In our third case study, we applied our same model to generalizations about causal events.
In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
In addition to further demonstrating the generality of this theory, these experiments show that the *prevalence prior* $P(h)$ is causally related to endorsements of generalizations in language.

@@

As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *prevalence*, or probability (Expt. 1, 2a \& 2b, 3).
This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.

@@

In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
We constructed the prior belief distribution for the prevalence of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
Thus, the prevalence prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.

@@

## Structured prior knowledge and Implications for Conceptual Structure

@@

Previous psychological and philosophical work on generics has looked beyond prevalence and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008]. 
Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
Where in the prevalence-based semantics could such conceptual distinctions come into play?

>>>>

abstract: > 
    Generalizations are central to human understanding and language provides simple ways to convey generalization (e.g., "Dogs bark").
    The language of generalization is ubiquitous in everyday discourse and child-directed speech. 
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    The major issue in formalizing generalizations in language is in determining what which such statements are true or false.
    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Dogs bark"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind"). 
    Across these diverse domains, we find that our model explains human endorsements of generalizations in language, while simpler models do not.
    This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
    The results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

keywords          : "genericity, generalization, generics, pragmatics, semantics, bayesian modeling"
wordcount         : "X"

@@

If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability. 
One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
For generalizations, the threshold would apply to the *feature-probability* $h$:^[
We emphasize that our account is based on an agent's subjective probability $h$. The literature on generic language has often examined *prevalence*, or the proportion of members of a category with the property, as the primary quantitative metric that could relate to generic meaning (in addition to *cue validity*, described below). A Bayesian agent, however, would only use prevalence as a way to update her existing state of knowldege to form a subjective probability for future use. Thus, we consider the semantic content of a generalization to be related to probability, not necessarily prevalence.
]

@@

From a methodological standpoint, habituals are a particularly convenient domain for manipulating the referent feature-probability that a speaker aims to communicate.^[
While referent feature-probability can be manipulated for generalizations about categories (e.g., by stating the prevalence of feature in a kind), observers may have strongly constraining domain knowledge that heavily guides what feature-probabilities are likely (e.g., it's *a priori* very unlikely that 90% of a hypothetical novel kind---lorches---have broken wings).
]
Due to the sociality of our species, we are often in the situation of being introduced to new people and learning new information about them.
In addition, feature-probabilities of people doing actions can be expressed in an easily-interpretable rate information (e.g., "Last month, Mary smoked cigarettes 3 times.").^[
In this case study, we use frequencies or rates of people doing actions (e.g., *smoking cigarettes 3 times a month*) as our feature-probabilities for ease of interpretability. 
A rate can be converted into a probability of the event occuring in some time window by computing the area under the curve of a Poisson distribution parametrized by the rate.
]

@@

Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely her observations. 
Up to this point, we have said little as to the interpretation of $h$, the referent feature-probability  that the speaker aims to convey.
In two follow-up experiments, we ask whether $h$ represents the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past week) or the predictive rate of this event occurring in the near future (e.g., how often we should expect Mary to smoke next week).
We do this by measuring particpants predictions about future rates where there are causal forces enabling or preventing the action (Expt. 2c). 
We separately measure endorsements under the same contexts (Expt. 2d) and use the prediction measurements (Expt. 2c) as the referent feature-probabilities $h$ that the speaker model is trying to communicate, in order to predict habitual endorsements.
To anticipate our results, we find that only a model that uses the *predictive* feature-probabilities as the object of communication is able to explain the endorsement data, thus tying the phenomenology of *genericity* even more to subjective beliefs.

@@

In this experiment we elicit the feature-probability prior $P(h)$ for different events in order to generate model predictions for corresponding habitual statements (Expt. 2b \& 2d).
For the case of statements about the behaviors of people, $P(h)$ can be conceived as a distribution over *different people*, each of whom do the behavior with different rates or probabilities.
To better understand what frequencies should be expected for different actions, we took advantage of the structured representation of the feature-probability prior discovered in Expt. 1.

@@

We next explore the endorsements of habituals from the items whose feature-probability priors were measured the prior elicitation task.

@@

habituals.endorsement.models <- bind_rows(
  d.hab.endorse.regression,
  left_join(
    m.hab.endorse.rsa %>% 
    rename(prediction = MAP, prediction_lower = cred_lower, prediction_upper = cred_upper),
    d.hab.endorse.regression %>% 
    select(habitual, time_period, logAnnualRate, mixture)
  )
) %>%
  mutate(src = factor(src, levels = c( 
                                      "some_model",
                                      "habituals_model",
                                      "regression_freq", 
                                      "regression_freq_distinct"
                                     ),
                      labels = c(
                                 "Speaker model - fixed semantics",
                                 "Speaker model - uncertain semantics",
                                 "Referent frequency alone", "Distinctiveness + referent frequency"
                                 ))) %>%
  ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 2)+
  theme(legend.position = "bottom")
```

@@

```{r habituals-endorsement-figure, fig.width=11, fig.height=8, fig.cap="Endorsing generalizations about events Top left: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action. Top right: Model fits for the uncertain semantics speaker model (upper right), a fixed semantics speaker model (upper left), and regression models based on referent (log) frequency alone (lower left) and referent log frequency + distinctiveness (lower right). Bottom: Five example frequency priors and listener posteriors upon hearing the generalization. These distributions are inferred using both data sources from Expts. 2a & 2b.  (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})"}
grid.arrange(fig.habituals.endorsement.vs.freq, 
             habituals.endorsement.models,
             habituals.endorsement.insets, ncol = 2,
             layout_matrix = cbind(c(1,1,3), c(2,2,3)))
```

<!-- For the six items for which data for characters of both genders were collected for each participant, we analyzed only the data from participants' first presentation of the item. -->
Parallel to our analysis of generic language endorsements, we articulate a set of simple regression models and an alternative to our uncertain-threshold RSA model in order to understand the data and our model.
For all analyses, we collapse across gender of the referent character.
<!-- Before comparing models, we perform an exploratory analysis on a subset of our data, exploring whether or not endorsements for items whose priors differed by gender will also differ. -->

@@

#### Referent frequency baseline

The simplest alternative hypothesis for habitual language endorsement is that the degree to which the habitual statement is acceptable is given by the referent frequency. 
This is unlikely to be the case based on Figure \ref{fig:habituals-endorsement-figure} (top-left), which shows the correspondence between the frequency of the event (transformed to a log times-per-year scale) and the human-judged felicity of the corresponding habitual sentence. 
First, it is clear that not all habitual statements are strongly assented to, even though it is true that all the stimuli involved an agent doing the action with some non-zero frequency (at least 3 times before).
It is also clear that a habitual sentence can receive strong agreement even when the actions are very infrequent (3 times in a 5-year interval; e.g., \emph{writes novels}, \emph{climbs mountains}), arguing against the second alternative.
We see in addition that even when actions are done relatively frequently (e.g., 3 times in a one month interval), some habitual sentences receive less than full endorsement (e.g., \emph{wears socks}, \emph{drinks coffee}). 
In our data, actions completed with a high frequency (3 times in a one week interval) receive at a minimum 75\% endorsement, though there is still variability among them (e.g., between 10-25\% of people disagree with \emph{wears a watch} and \emph{wears a bra}).
Overall, the referent log-frequency of action predicts only a fraction of the variability in responses ($r^2(`r r2.hab.n`) = `r r2.habituls.regression.freq`$; MSE=$`r mse.habituls.regression.freq`$). 
In addition, for actions that are done on the time scale of years or longer (lower median of frequency), referent frequency no longer explains the endorsements ($r^2(`r r2.hab.infrequent.n`) = `r r2.habituls.infrequent.regression.freq`$; MSE =$`r mse.habituls.infrequent.regression.freq`$)

In addition, we observe that none of our items receive less than 25\% endorsement (i.e., a maximum of about 75\% of participants disagree with the felicity of the utterance).
This reflects the fact that these statements are not altogether *false* even though the action is done very rarely.

#### Distinctiveness and referent frequency

In the prior elicitation task (Expt. 2a), we saw that items differed in both their mean expected frequency as well as the proportion of people who have done / do the action (i.e., the mixture parameter in the frequency prior $P(h)$).
With generics, we constructed a regression model that used empirical *cue validity* as a predictor of generic endorsement. 
Here, we articulate a regression model that uses participants' responses to the question about the mixture parameter $\phi$ (i.e., the proportion of people who have done the action before) to predict habitual endorsement. 
This is analagous to the regression model based on cue validity and referent feature-probability in the domain of generics.

@@

We used the speaker model $S_1$ (Eq. \ref{eq:S1}) with the priors elicited above (Expt. 2a) to predict felicity judgments in Expt. 2b, assuming the referent feature-probability $h$ being conveyed by $S_1$ is the provided frequency (e.g., 3 times in the past year).
Because we observe no difference between the felicity judgments for habituals of male and female characters, we use a 50\% mixture of the inferred priors for each gender to construct a single frequency distribution $P(h)$ across individuals.
The RSA model has a single free parameter---the speaker optimality parameter, $\alpha_1$, in Eq. \ref{eq:S1}. 
As we did for the generics case study, we use Bayesian data analytic techniques to integrate over these parameters \cite{LW2014}, comparing the posterior predictive distribution to the empirical data in Expt. 2b.
To construct the posterior predictive distribution over responses, we collected 2 MCMC chains of 100,000 iterations, discarding the first 50,000 iterations for burn in.
<!-- The Maximum A-Posteriori value and 95\% highest probability density interval for $\alpha_1$ is 19.3 [14.9,19.9] and $\alpha_2$ is 1.5 [1.4,1.6]. -->

@@

In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
This raises an interesting question: Does the feature-probability communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).

@@

While past frequency is often a good indicator of future tendency, people change abruptly due to a variety of decisions and outside events.
Does habitual language communicate probabilities in terms of past frequency or future expectations?
On one hand, speakers can only *know* about what has happened in the past.
On the other hand, language has a communicative function, and it would seem useful for speakers to convey what they *believe* will be the case in the future.

@@

<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
In Experiments 2c \& 2d, we further investigated the nature of the underlying feature-probability scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt. 2c) and using that, with the model, to predict the felicity of habitual sentences (Expt. 2d). 
To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of such generalizations in language.

In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while still measuring the priors over the feature-probability for the event.
Thus, it is still possible that the feature-probability priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlationally associated with generic and habitual endorsement but not directly causally related.
In our final case study, we extend our theory to communicating generlizations about causes, and experimentally test whether the feature-probability priors are indeed causally related to endorsing generalizations in language.

@@

Language provides a way to bypass the observational data needed to make a causal induction.
Indeed, causal language faciliates causal learning for nonobvious causal relations in children as young as 2-years-old [@Bonawitz2010].

In this paper, we posit that feature-probability priors are a mediating representation between abstract conceptual structure and generalizations in language.
In this last set of experiments, we test the causal relationship between the feature-probability priors and endorsements of generalizations about causes.
Also, by designing the experiments in the domain of causal language, we further demonstrate the generality of our theory of communicating generalizations.

@@

## Experiment 3a: Manipulating the feature-probability priors for causes

In this experiment, we introduce participants to statistics about novel causal forces and have them make predictions about future instances of those causes.
This prediction task serves as a manipulation check for our feature-probability prior manipulation.

@@

The experiment is a single-trial experiment with 2 phases to the trial.
In the first phase, participants are given a story about a causal domain.
In the second phase, participants are asked to make a judgment corresponding to either the prior task or the endorsement task (described below).

@@

causals.endorsement.insets <- cas.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, 
                              levels = c("state_Prior","state_Posterior"),
                            labels = c("Listener Prior (Posterior given Silence)",
                                       "Listener Posterior given Causal")),
    Distribution = factor(distribution, 
                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
         labels = c("Common Deterministic", "Rare Deterministic",
                    "Common Weak", "Rare Weak"))) %>%
  ggplot(., aes( x = value, fill = Distribution, color = Distribution, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~Distribution, nrow = 1)+
  scale_fill_manual(values =inset.color.order )+
  scale_color_manual(values = inset.color.order)+
  scale_alpha_manual(values = c(0.1, 0.8))+
  scale_linetype_manual(values = c(2, 1))+
  scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Feature-probability") +
  ylab("Scaled probability density")+
  theme(legend.position = "bottom", legend.title = element_blank())+
  guides(fill = F, color = F)
```

@@

```{r figure-causals, fig.width=11, fig.height=8, cache = T, fig.cap="Endorsing generalizations about causes. Top: Human elicited endorsements and model fit predictions for four manipulated prior distributions and two observed frequencies. Bottom: Feature-probability priors and listener posteriors upon hearing the generalization for the experimentally manipulated priors. These distributions are inferred using both data sources from Expt. 3 (analagous to the Bayesian data analytic approach outlined in Figure \\ref{fig:genericsModelDiagram})."}
grid.arrange(figure.causals.endorsement, causals.endorsement.insets, ncol = 1,
             layout_matrix = cbind(c(1,1,2)))

@@

In our third case study, we applied our same model to generalizations about causal events.
In this domain, we succesfully manipulated participants' beliefs about the expected causal power in a domain (Expt. 3a).
We did this for both unstructured distributions (*common weak*, *common strong*) and structured distributions (*rare weak*, *rare strong*). 
In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
In addition to further demonstrating the generality of this theory, these experiments show that the *feature-probability prior* $P(h)$ is causally related to endorsements of generalizations in language.
To our knowledge, these are the first experiments to demonstrate how the probabilities of other categories having a feature can influence endorsing a generalization about a different category.

@@

As a formal theory of generalizations in language, we aim to unify significant swaths of language that are seemingly quite different from one another: generalizations about categories, events, and causes.
What these expressions have in common is not surface-level features but *genericity*, the fact that these statements convey generalizations. 
Indeed we have been able to capture the context-sensivity of these statements by positing a single underlying scale defined by the *feature-probability* (Expt. 1, 2a \& 2b, 3).
This scale is defined by a subjective, predictive probability, not mere frequency (Expts. 2c \& 2d).
We have shown that listeners' prior knowledge about this scale is causally related to their endorsement of statements of genericity (Expt. 3).
Finally, our framework naturally accounts for a number of well-documented examples from the linguistics of generalizations about categories, or *generic language* (Expt. 1).
In addition to unifying seemingly disparate parts of language, this paper provides a theoretical framework for asking further questions about genericity, which we outline below.

@@

In this paper, we proposed a model for understanding generalizations in language that relies upon interlocutors' shared beliefs over the statistics of the event or property under discussion.
We constructed the prior belief distribution for the probability of a property, event, or cause by considering other possible categories having the property, people doing the action, or causes producing the effect.
These other kinds, people, and causes form *comparison classes* against which the referent-category is evaluated. 
Thus, the feature-probability prior $P(h)$ is always relative to a class of other entities or events, a comparison class $C$: $P_C(h)$.

@@

## Structured prior knowledge and implications for conceptual accounts

@@

Previous psychological and philosophical work on generics has looked beyond feature-probability and focused on conceptual distinctions and relations [@Gelman2003; @Prasada2013; @Leslie2007; @Leslie2008].^[
In these accounts, feature-probability is normally treated as synonymous with the current *prevalence* of the feature in the category. 
As we have shown, feature-probability in our account is more general notion, reflecting speaker's subjective, predictive probabilities.
] 
Prasada has argued for a distinction between \emph{characteristic} properties (e.g., \emph{Diapers are absorbent.}) and \emph{statistical} properties (e.g., \emph{Diapers are white.}).
Leslie suggests information that is striking (e.g., \emph{Tigers eat people.}) is useful and thus permitted to be a generic.
Gelman outlines how generics tend to express \emph{essential} qualities that are relatively timeless and enduring. 
Where in the probability-based semantics could such conceptual distinctions come into play?
